Papers

### 2023-05-26 quarto/index.qmd
update

**Aston Zhang** is a senior scientist at Amazon Web Services AI Research.
He studies efficient and robust methods for machine learning and natural language processing, currently focusing on large language models.
He received the <a href="https://iclr-conf.medium.com/announcing-iclr-2021-outstanding-paper-awards-9ae0514734ab" target="_blank">ICLR Outstanding Paper Award (2021)</a>,
the ACM Ubicomp Distinguished Paper Award (2018), and the ACM SenSys Best Paper Award Nomination (2017).
His <a href="https://github.com/d2l-ai" target="_blank">open-source</a> textbook,
<a href="https://d2l.ai" target="_blank">Dive into Deep Learning</a>,
has been <a href="https://d2l.ai/_images/map.png" target="_blank">adopted worldwide</a>.
He obtained his Ph.D. in Computer Science from University of Illinois at Urbana-Champaign.

>>>>

**Aston Zhang** is a scientist at Amazon Web Services AI Research.
He studies language models and multimodality for AI.
He received the <a href="https://iclr-conf.medium.com/announcing-iclr-2021-outstanding-paper-awards-9ae0514734ab" target="_blank">ICLR Outstanding Paper Award (2021)</a>,
the ACM Ubicomp Distinguished Paper Award (2018), and the ACM SenSys Best Paper Award Nomination (2017).
His <a href="https://github.com/d2l-ai" target="_blank">open-source</a> textbook,
<a href="https://d2l.ai" target="_blank">Dive into Deep Learning</a>,
has been <a href="https://d2l.ai/_images/map.png" target="_blank">adopted worldwide</a>.
He obtained his Ph.D. in Computer Science from University of Illinois at Urbana-Champaign.
